Corrections to Manuscript No. 15-TIE-3480

### 2016-03-27 RMS/corrections.tex
first version done for major revision

\usepackage{alltt}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{multicol}
\newcommand{\hide}[1]{\ignorespaces}
\newcommand{\jx}[1]{{\bf Jiaxiang: }#1{ \bf End}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

@@

1) The weak point is the lack of evidence of practicality, efficiency
and scalability. Since there are only small and simplistic scenarios
to analyze this model, it is difficult to judge the effectiveness of
the proposed implementation. The key scenarios appear conveniently
small to allow the implementation fully supports all these examples,
returning at the same time appropriate counterexamples to guide and
adjust the design. Is this true for larger examples of "real world"
applications within the field of industrial real-time systems? How do
the authors propose to handle very large scenarios? ¿How does it
behave on typical real-time scheduling problems used in industry? I
would like to see more complex examples to convince the reader of the
practicability of the approach on the assumptions given for the model,
and would probably increase the mentioned benefits. The paper does not
give any directions to the above problems, and some sentences pointing
out the difficulties in the implementation of more generic and
realistic scenarios would be most welcome to understand the real
contribution of the paper.

ANSWER: TODO

@@

ANSWER: The detailed proof is now included in the appendix. It is true
that readers may be interested in the detailed proof of Theorem~2 to
feel convinced of the completeness of our approach. However, the proof
needs a bit more theoretical background about rewriting logic and more
details of our model, which we have simplified in the submission to
ease the understanding of our approach. We would prefer to refer the
detailed proof to a non-anonymous technical report, if possible, in
the final version.

@@

ANSWER: TODO. To revise the modeling section.

@@

ANSWER: The related work section is now improved. More comparisons
with the theoretical approaches and with [24,25] are added. The
differences with [24,25] in the models and in the way of modeling are
mainly discussed. On the other hand, it is a bit difficult to compare
the efficiency and scalability between [24,25] and our approach. One
reason is that we have a different setting with [24] and [25], because
the objectives are different: we aim at verifying an RMS implemention
from a real-world real-time system, while [24] and [25] targeted the
RMS algorithm itself. Another reason is that [24] and [25] presented
no discussion on the efficiency and scalability. Furthermore, they use
\verb|TMSVL| and an extension of SPIN, respectively, as verification
tools, which are not open-source, making it unable to re-implement
their work.

@@

ANSWER: The statement has been corrected. The work presented in this
submission aims at modeling and verifying a realistic RMS
implementation in an industrial avonic system. It is a piece of real
work in the industry. Even though we believe that our approach could
be applied to other systems as well, it means more to that specific
one. In this sense, ``sufficient'' means that the details described in
our model meet the requirements and expectations from the users and
the engineers.

@@

ANSWER: TODO. to make the paper self-contained.

@@

ANSWER: Yes, we agree that we have two choices to do the work
presented in the paper: one is to develop a general way to model RMS
algorithms or implementations, and then instantiate the general model
to get a concrete one for our target system; the other is to shape an
accurate model of the target system directly. To us, there is a trade
off between these two directions. We chose the latter with some
concerns. By our experience, the engineers, who write the codes, and
those, who are in charge of verifying the system or the codes, are
usually not the same persons. When a verification engineer models a
system, he is actually abstacting the system or the codes. It is
difficult to ensure that the model behaves the same as the system or
the codes.  And it is more difficult to let other engineers and users
believe that the model behaves the same as the system or the
codes. Furthermore, the developers and users hope that the model
behaves not only the same as what they had in mind, but also the same
as what is written in the codes. A way out is to make the model not
only behave like the codes, but also ``look'' like the codes. This
requires the model to be as accurate as possible. It makes the model
specific, but improves the engineers' confidence in the model and the
verification results. That is also why we emphasize the
correspondences between the functions in the model and the lines in
the pseudocode, when we introduce our model in Section~IV. On the
other hand, we are also interested in the first choice. This will be
the future work and we would try to get a better balance between them.

@@

ANSWER: The section about soundness and completeness is now made more
self-contained. The detailed proof of Theorem~2 is included in the
appendix. On the other hand, since we chose the accurate way to
achieve the model as discussed above, yes, the proof is a specific
one.

@@

ANSWER: TODO

@@

ANSWER: TODO

@@

ANSWER: It is done.

@@

ANSWER: TODO

@@

ANSWER: TODO

@@

ANSWER: TODO

@@

ANSWER: TODO

@@

ANSWER: The detailed proof is now included in the appendix.  The
detailed proof requires a bit more theoretical background about
rewriting logic and more details of our model, which we tried to
simplify in the submission to ease the understanding of our
approach. We would prefer to refer the detailed proof to a
non-anonymous technical report, if possible, in the final version.
\end{itemize}

@@

ANSWER: We agree that RMS is a very simple scheduling and is the
optimum at the same time among the fixed-prority ones, making it
widely applied and sufficiently investigated. Besides the ideal
setting, the schedulability of RMS was also investigated under
different kinds of implementations with consideration about overhead,
as we discuss in the related work section (Section VI). Despite the
reason that the existing results do not fit our target system using
RMS, the most important motivation to develop the work presented is
that, we aim at verifying the system not only for the schedulability,
but also for the correctness. That is, we want to verify that the
target system does schedule the tasks under the RMS algorithm. The
work presented should be seen as a verification problem, instead of a
schedulability test.

@@

ANSWER: The comparison is given in the related work section (Section
VI). We would say that we are not implementing RMS algorithm in
Real-Time Maude. In fact, we are using Real-Time Maude to model an
realistic implementation of RMS from an industrial avionic
system. There is no theoretical reason telling us that we have to use
Real-Time Maude to model the RMS implementation. However, the existing
verification work as far as we know cannot fit our needs, as discussed
in Section VI. Therefore, we developed the work in the paper, as a
piece of real work in the industry.

@@

ANSWER: As an industrial application, we are not trying to make the
problem as difficult as possible. Instead, we are trying to simplify
the model so that the existing tools are able to solve, while the
target system satisfies the assumptions on the model so that the
verification results are trustworthy. On the other hand, the
assumptions are not so rigid. For example, the mask mechanism
considered as hardware details makes the job initiation times of task
$\tau_i$ possibly not equal to $kT_i$, implying that the deadlines of
the jobs may be not equal to $(k+1)T_i$ (see assumption A1'). Another
example is that non-determinism exists in our model, as discussed in
Section VI.

@@

ANSWER: Yes, we agree that this is an application of rewriting
logic. In this paper, we do apply the existing theories and techniques
of rewriting logic to solve a real industrial problem, which has not
yet been investigated by this sort of techniques, achieving an
industrial contribution.

@@

ANSWER: We do not agree that we should illustrate the mechanism behind
the model checking commands, since the model checker is not part of
our contributions in the paper.

@@

ANSWER: ?

>>>>

\usepackage{alltt}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{multicol}
\newcommand{\hide}[1]{\ignorespaces}
\newcommand{\jx}[1]{{\bf Jiaxiang: }#1{ \bf End}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newcommand{\ANSWER}{{\bf ANSWER}}

@@

1) The weak point is the lack of evidence of practicality, efficiency
and scalability. Since there are only small and simplistic scenarios
to analyze this model, it is difficult to judge the effectiveness of
the proposed implementation. The key scenarios appear conveniently
small to allow the implementation fully supports all these examples,
returning at the same time appropriate counterexamples to guide and
adjust the design. Is this true for larger examples of "real world"
applications within the field of industrial real-time systems? How do
the authors propose to handle very large scenarios? How does it behave
on typical real-time scheduling problems used in industry? I would
like to see more complex examples to convince the reader of the
practicability of the approach on the assumptions given for the model,
and would probably increase the mentioned benefits. The paper does not
give any directions to the above problems, and some sentences pointing
out the difficulties in the implementation of more generic and
realistic scenarios would be most welcome to understand the real
contribution of the paper.

\ANSWER: As mentioned in the paper, the modeled RMS implementation
serves in an avionic control systems from our industrial partner. It
is a real-world application within the field of industrial real-time
systems. And the scenarios presented in Section V.B are also real
scenarios that our partner is using in the system. Our partner
indicated that there would be at most $5$ tasks in the task set for
the implementation. On the other hand, in the current version, we have
randomly generated large numbers of test cases to examine the
efficiency of our schedulability test that is based on model checking,
as discussed in Section V.B. The capability of model checking is
restricted by the scale of the state space of the model. In our model,
the model checking can handle scenarios where $mn$ is up to $10^6$ in
an acceptable period of time. With $mn=10^6$ and reasonable task
periods, the number $n$ of tasks can be at least $10$, which has
already fulfilled the requirements of the target
implementation. Further with particular task periods, the number $n$
of tasks can be $20$ or more.

@@

\ANSWER: The detailed proof is now included in the Appendix. It is true
that readers may be interested in the detailed proof of Theorem~2 to
feel convinced of the completeness of our approach. However, the proof
needs a bit more theoretical background about rewriting logic and more
details of our model, which we have simplified in the submission to
ease the understanding of our approach. We would prefer to refer the
detailed proof to a non-anonymous technical report, if possible, in
the final version.

@@

\ANSWER: Thank you for the invaluable suggestions. Section IV has been
revised. Some unnecessary detailed definitions presented as codes are
removed, and replaced by more explanations. We hope that the current
presentation would make Section IV more easy-to-read, even for an
audience who does not know Real-Time Maude before. On the other hand,
Section VI (Related Work) is also improved. We compare our work with
the existing theoretical work and the existing verification work in a
more complete way.

@@

\ANSWER: The related work section is now improved. More comparisons
with the theoretical approaches and with [24,25] are added. The
differences with [24,25] in the models and in the way of modeling are
mainly discussed. On the other hand, it is a bit difficult to compare
the efficiency and scalability between [24,25] and our approach. One
reason is that we have a different setting with [24] and [25], because
the objectives are different: we aim at verifying an RMS implemention
from a real-world real-time system, while [24] and [25] targeted the
RMS algorithm itself. Another reason is that [24] and [25] presented
no discussion on the efficiency and scalability. Furthermore, they use
\verb|TMSVL| and an extension of SPIN, respectively, as verification
tools, which are not open-source, making it unable to re-implement
their work.

@@

\ANSWER: The statement has been corrected. The work presented in this
submission aims at modeling and verifying a realistic RMS
implementation in an industrial avonic system. It is a piece of real
work in the industry. Even though we believe that our approach could
be applied to other systems as well, it means more to that specific
one. In this sense, ``sufficient'' means that the details described in
our model meet the requirements and expectations from the users and
the engineers.

@@

\ANSWER: The Sections II.B and IV are improved to be more
self-contained now. The idea is that, Section II.B contains mainly an
overview of Real-Time Maude, and then Section IV describes the model
with introducing necessary syntax on-the-fly.

@@

\ANSWER: Yes, we agree that we have two choices to do the work
presented in the paper: one is to develop a general way to model RMS
algorithms or implementations, and then instantiate the general model
to get a concrete one for our target system; the other is to shape an
accurate model of the target system directly. To us, there is a trade
off between these two directions. We chose the latter with some
concerns. By our experience, the engineers, who write the codes, and
those, who are in charge of verifying the system or the codes, are
usually not the same persons. When a verification engineer models a
system, he is actually abstacting the system or the codes. It is
difficult to ensure that the model behaves the same as the system or
the codes.  And it is more difficult to let other engineers and users
believe that the model behaves the same as the system or the
codes. Furthermore, the developers and users hope that the model
behaves not only the same as what they had in mind, but also the same
as what is written in the codes. A way out is to make the model not
only behave like the codes, but also ``look'' like the codes. This
requires the model to be as accurate as possible. It makes the model
specific, but improves the engineers' confidence in the model and the
verification results. That is also why we emphasize the
correspondences between the functions in the model and the lines in
the pseudocode, when we introduce our model in Section~IV. On the
other hand, we are also interested in the first choice. This will be
the future work and we would try to get a better balance between them.

@@

\ANSWER: The section about soundness and completeness is now made more
self-contained. The detailed proof of Theorem~2 is included in the
appendix. On the other hand, since we chose the accurate way to
achieve the model as discussed above, yes, the proof is a specific
one.

@@

\ANSWER: Yes, they can be states. But more generally, they are
terms. This part has been modified to specify $s$ and $s'$ ($t$ and
$t'$ now) clearly.

@@

\ANSWER: Thanks very much for reminding. This is added now.

@@

\ANSWER: It is done.

@@

\ANSWER: Sorry for missing the explanation of \verb|[ctor]|. It is now
added when \verb|[ctor]| is used for the first time.

@@

\ANSWER: Sorry for the misleading in the text. In fact, \verb|bottom|
and \verb|#| are constructors of sort \verb|Stack|. This part is
modified now. Some detailed definitions in codes are removed, and are
replaced by more explanations. We hope that the current presentation
would make Section IV more easy-to-read.

@@

\ANSWER: Sorry for this incompleteness. \verb|NzNat| did mean non-zero
natural numbers. \verb|NzNat| is now replaced by \verb|Nat| to reduce
unnecessary complexity for the readers.

@@

\ANSWER: In fact, the definitions of time-robustness and
tick-stabilization (which is now replaced with tick-invariance)
require more knowledge about rewriting logic. We avoid introducing the
accurate definitions of them. Instead, we now give short descriptions
of them. More detailed introduction can be found in the Appendix.

@@

\ANSWER: The detailed proof is now included in the appendix.  The
detailed proof requires a bit more theoretical background about
rewriting logic and more details of our model, which we tried to
simplify in the submission to ease the understanding of our
approach. We would prefer to refer the detailed proof to a
non-anonymous technical report, if possible, in the final version.
\end{itemize}

@@

\ANSWER: We agree that RMS is a very simple scheduling and is the
optimum at the same time among the fixed-prority ones, making it
widely applied and sufficiently investigated. Besides the ideal
setting, the schedulability of RMS was also investigated under
different kinds of implementations with consideration about overhead,
as we discuss in the related work section (Section VI). Despite the
reason that the existing results do not fit our target system using
RMS, the most important motivation to develop the work presented is
that, we aim at verifying the system not only for the schedulability,
but also for the correctness. That is, we want to verify that the
target system does schedule the tasks under the RMS algorithm. The
work presented should be seen as a verification problem, instead of a
schedulability test.

@@

\ANSWER: The comparison is given in the related work section (Section
VI). We would say that we are not implementing RMS algorithm in
Real-Time Maude. In fact, we are using Real-Time Maude to model an
realistic implementation of RMS from an industrial avionic
system. There is no theoretical reason telling us that we have to use
Real-Time Maude to model the RMS implementation. However, the existing
verification work as far as we know cannot fit our needs, as discussed
in Section VI. Therefore, we developed the work in the paper, as a
piece of real work in the industry.

@@

\ANSWER: As an industrial application, we are not trying to make the
problem as difficult as possible. Instead, we are trying to simplify
the model so that the existing tools are able to solve, while the
target system satisfies the assumptions on the model so that the
verification results are trustworthy. On the other hand, the
assumptions are not so rigid. For example, the mask mechanism
considered as hardware details makes the job initiation times of task
$\tau_i$ possibly not equal to $kT_i$, implying that the deadlines of
the jobs may be not equal to $(k+1)T_i$ (see assumption A1'). Another
example is that non-determinism exists in our model, as discussed in
Section VI.

@@

\ANSWER: Yes, we agree that this is an application of rewriting
logic. In this paper, we do apply the existing theories and techniques
of rewriting logic to solve a real industrial problem, which has not
yet been investigated by this sort of techniques, achieving an
industrial contribution.

@@

\ANSWER: We do not agree that we should illustrate the mechanism behind
the model checking commands, since the model checker is not part of
our contributions in the paper.

@@
